Higher-Order unification for free!

### 2024-04-25 paper/main.tex
add comment to simulation and fidelity

>>>>

In \cref{sec:llam,sec:eta,sec:beta,sec:invariant1}, we will ensure
\Cref{prop:fidelity}, since we consider this property quite important. Our aim
is to guarantee that the success of \hstep coincides with the success of \fstep
at each step $p$, regardless of any newly introduced modifications in our
unification process. We postpone the discussion of \Cref{prop:fidelity-recovery}
to \cref{sec:beta}, where we delve into unifications involving terms outside
\llambda. Moreover, we reserve the proof of \Cref{prop:simulation} only in
\cref{sec:llam}, due to the absence of links. In the other sections, we omit the
proof of this latter property due to space constraints. However, the underlying
idea remain constant: link activation refines $\sigma$ so that if $\rho_i
\foUnifPb_{i_l} \Uo \sigma_i \foUnifPb_{i_r}$ then $\sigma_i \hoUnifPb_{i_l} \Ue
\sigma_i \hoUnifPb_{i_r}$. Finally, \D{\sigma_n}{\mapStore}{\linkStore_n}{\rho}
and $\rho$ is equivalent to the substitution returned by $\frun(\foUnifPb,n)$.
